---
title: "HELPrct (Data Verbs) Activity"
author: "Names of BOTH partners"
date: "Due Date"
output: html_notebook
---


## Set Up:

```{r}
# load packages
library(tidyverse)  # includes lots of data verbs like `group-by()` and `summarise()`
library(mosaicData) # includes the `HELPrct data set 
library(mosaic)     # includes the `mplot()` interactive plot builder

# Load the HELPrct data set into our RStudio environment
data("HELPrct")

```


## Data Description

*Task 1: Write a couple of sentences describing the `HELPrct` data--What is the setting for the data? What are they about?* 


## Basic Summaries with `summarise()` 

*Task 2: Produce an expression involving `summarize()` and `HELPrct` that will produce the following.*

- *number of people (cases) in `HELPrct` study*
- *combined total number of times in the past 6 months all the people in `HELPrct` entered a detox program (measured at baseline)* 
- *mean time (in days) to first use of any substance post-detox for all the people in `HELPrct`*


```{r}

```


## Subgrouping with `group_by()` 

*Task 2: Repeat task 1 above, but calculate the results group-by-group.  Show your code and write a sentence or two about what you observe in the results for each of the following:* 

1. *males versus females*

```{r}

```


2. *homeless or not*

```{r}

```

3. *substance*

```{r}

```

4. *break down the homeless versus housed further, by sex*

```{r}

```

5. *break down the homeless versus housed further, by substance*

```{r}

```


## Task 3:

*Include one or more interesting plots of the data involving at least 3 variables per plot. Write a few sentances to explain the story that your plot tells about these data.  You can use one of the relationships that you studied in Task 2, or you can explore a different group of variables in the HELPrct that show something interesting.*  



```{r}

```


